---
title: "Analysis"
subtitle: "From [PROJECT](https://github.com/katekathrynkat/PROJECT)"
output:
  katereR::t_analysis
---

**Kate Culhane**, Dept. of Ecology, Evolution, and Marine Biology, UC Santa Barbara  
[kathrynculhane@ucsb.edu](kathrynculhane@ucsb.edu)
[<i class="fa fa-github"></i>](https://github.com/katekathrynkat/)
[<i class="fa fa-twitter"></i>](https://twitter.com/katekathrynkat/)

***

```{r setup, include=FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_knit$set(root.dir='..')
knitr::opts_chunk$set(echo=TRUE, results='hold', warning=FALSE, message=FALSE,
                      fig.width=5, fig.height=3, rows.print=5)
```

<div class = "summary">

**SUMMARY**

Brief summary goes here

</div>

***

**DEPENDENCIES**

```{r dependencies, class.source='fold-show'}

##### PACKAGES #####

# library(tidyverse) # data manipulation & visualization
# library(katereR) # my favorite ggplot themes

##### SOURCE CODE #####

# source('R_scripts/FILE_NAME.R')

##### DATA #####

# Brief description
# read_csv()

```

**OUTPUT FILES**

- **file_name.ext**: Brief description

## Important things

<div class = "important">

Something important

</div>

> Note about something to check later

## Tabbed section {.tabset .tabset-fade .tabset-pills}

Summary

### Tab 1

### Tab 2

### Tab 3

## Notes & resources

- [Webpage](link), author

<br>
<br>
<br>

***

<details><summary>**SESSION INFO**</summary>
```{r session-info}
devtools::session_info()
```
</details>
